Choose a License

### 2024-09-21 choose_license.qmd
Fix typo

When you have your article published under an open access license, some publishers still demand an exclusive publishing and distribution license or a copyright assignment. This would give them more rights than the readers of the article have through the chosen open access license [@Rumsey2022], and exceeds exceeds by far what is necessary to make publication possible [@Suber2022]. Consequently, authors should oppose this practice and grant publishers the same rights that every other reader of the article has. If your chosen publisher insists on an exclusive license, you may at least retain the copyright for your figures -- follow the guide "Retaining copyright for figures in academic publications to allow easy citation and reuse" by @Elson2016 to learn how to do that.

>>>>

When you have your article published under an open access license, some publishers still demand an exclusive publishing and distribution license or a copyright assignment. This would give them more rights than the readers of the article have through the chosen open access license [@Rumsey2022] and exceeds exceeds by far what is necessary to make publication possible [@Suber2022]. Consequently, authors should oppose this practice and grant publishers the same rights that every other reader of the article has. If your chosen publisher insists on an exclusive license, you may at least retain the copyright for your figures -- follow the guide "Retaining copyright for figures in academic publications to allow easy citation and reuse" by @Elson2016 to learn how to do that.
